Communication Efficient Learning towards Crowdsourcing Applications

### 2017-04-11 draft/draft.tex
- rewrite the abstract

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure} 
%\usepackage{subfig}%[caption=false,font=footnotesize]

@@

%-------------------------------------------------------------
%                      Own Commands
%-------------------------------------------------------------
\usepackage{amsmath}
\newcommand{\cbn}{\textsc{Cbn}}
\newcommand{\bn}{\textsc{Bn}}

\renewcommand{\algorithmiccomment}[1]{/* #1 */}
\def\ci{\perp\!\!\!\perp}
\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
% Theorem & Co environments and counters
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem{equat}[theorem]{Equation}
%\newtheorem{example}[theorem]{Example}
%-------------------------------------------------------------

@@

\begin{abstract}
submit  abstract until 13.04

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure} 
\usepackage{color}
%\usepackage{subfig}%[caption=false,font=footnotesize]

@@

%-------------------------------------------------------------
%                      Own Commands
%-------------------------------------------------------------
\usepackage{amsmath}
\newcommand{\cbn}{\textsc{Cbn}}
\newcommand{\bn}{\textsc{Bn}}
\newcommand{\huang}[1]{\textcolor{blue}{#1}}
\newcommand{\mycomment}[1]{\textcolor{red}{( ...#1 )}}
\renewcommand{\algorithmiccomment}[1]{/* #1 */}
\def\ci{\perp\!\!\!\perp}
\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
% Theorem & Co environments and counters
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem{equat}[theorem]{Equation}
%\newtheorem{example}[theorem]{Example}
%-------------------------------------------------------------

@@

\begin{abstract}
Learning from multiple sources of labeled data can increase the confidence of a machine learning system, 
%if the expertise of different labelers can efficiently \huang{properly} be assembled. 
however, 
%using 
\huang{employing } a large amount of labelers in the test time can be expensive \huang{in} the long run. For instance, in crowdsourcing we have to pay each labeler in order to get the annotations. In 
% a scenario of 
Internet-of-Things, 
obtaining data from multiple sensors \huang{for direct fusion } 
incurs high communication overhead. 
%Nevertheless, in many situations a small subset of 
%%competent experts 
%data sources could already 
%%constitute a very accurate labeling system
%deliver reliable annotations, \huang{thus we reduce the cost of communication with other labelers effectively}. 
\huang{In this paper}, we 
%design a methodolojgy
propose a method for training a classification system 
%where data labels are obtained from a small set of labelers and the labelers are weighted optimally in order to offer high classification accuracy. 
\huang{from multiple annotated training data, where only a small subset of labelers are optimally chosen to reduce communication effort.} We define an iterative optimization procedure where the sparsity of a client vector \huang{is computed} to reweigh the labelers 
%is controlled 
while reducing the overall classification error. 
%Using this procedure, 
\huang{In experiments, we show that our approach 
%obtain results close to 
can pertain the classification performance as on the complete set of labelers, while reducing 
%the number of those 
the communication effort by over 60\% on several different tasks.}

%submit  abstract until 13.04
